Plots

### 2025-10-20 src/plots.Rmd
Finish gpt5 revisions, finish reviewer1 responses, working on reviewer2 responses

# Plot perf of models using trend lines
plot_perf_trend <- function(
        df_long,
        f = calc_pccc,
        group = "age_range",
        text_scale = 1,
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        title_size = 10,
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        legend_text_size = 9 * text_scale,
        legend_position = "bottom",
        legend_direction = "horizontal",
        legend_spacing = unit(0, "pt"),
        x_color_labels = c(
            "G3" = "GPT-3.5",
            "G4" = "GPT-4",
            "G5" = "GPT-5",
            "ISV" = "InSilicoVA",
            "I5" = "InterVA-5"
        ),
        x_linetypes = c(
            "solid",
            "solid",
            "dashed",
            "dotted",
            "dotted"
        ),
        plot_mean = F
    ) {

@@

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(
            aes(
                linetype = model_name,
                alpha = model_name
            ),
            linewidth = 1.15
        ) + 
        scale_color_manual(
            values = default_colors,
            labels = x_color_labels
        ) +
        scale_linetype_manual(
            values = x_linetypes,
            labels = x_color_labels
        ) +
        scale_alpha_manual(
            values = c(1, 0.35, 0.9, 0.9),
            labels = x_color_labels
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.key.width = unit(32, "pt"),
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf_bar(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult, 12+ Years (n=", n_adult, ")"),
    text_scale = 0.7,
    x_hpos = -0.15,
    x_expand = expansion(add = 0.15)
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf_bar(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child, 28 Days to 11 Years (n=", n_child, ")"),
    text_scale = 0.92,
    x_hpos = -0.24,
    x_expand = expansion(add = 0.25)
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf_bar(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal, <28 Days (n=", n_neo, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.92,
    x_hpos = -0.24,
    x_expand = expansion(add = 0.25)
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    y_title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.9
)

>>>>

# Plot perf of models using trend lines
plot_perf_trend <- function(
        df_long,
        f = calc_pccc,
        group = "age_range",
        text_scale = 1,
        title = NULL,
        x_title = NULL,
        y_title = NULL,
        title_size = 10,
        x_title_size = 9 * text_scale,
        y_title_size = 9 * text_scale,
        x_text_size = 8 * text_scale,
        y_text_size = 9 * text_scale,
        legend_text_size = 9 * text_scale,
        legend_position = "bottom",
        legend_direction = "horizontal",
        legend_spacing = unit(0, "pt"),
        y_limits = c(0, 1.15),
        y_breaks = seq(0, 1, by = 0.1),
        x_color_labels = c(
            "G3" = "GPT-3.5",
            "G4" = "GPT-4",
            "G5" = "GPT-5",
            "ISV" = "InSilicoVA",
            "I5" = "InterVA-5"
        ),
        x_linetypes = c(
            "solid",
            "solid",
            "dashed",
            "dotted",
            "dotted"
        ),
        x_linealpha = c(
            1,
            0.5,
            0.9,
            0.9,
            0.7
        ),
        x_linewidths = c(
            2,
            1,
            1.15,
            2,
            1.15
        ),
        plot_mean = F
    ) {

@@

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(
            aes(
                linetype = model_name,
                alpha = model_name,
                linewidth = model_name
            )
        ) + 
        scale_y_continuous(
            limits = y_limits,
            breaks = y_breaks
        ) +
        scale_color_manual(
            values = default_colors,
            labels = x_color_labels
        ) +
        scale_linetype_manual(
            values = x_linetypes,
            labels = x_color_labels
        ) +
        scale_linewidth_manual(
           values = x_linewidths,
           labels = x_color_labels
        ) +
        scale_alpha_manual(
            values = x_linealpha,
            labels = x_color_labels
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.key.width = unit(32, "pt"),
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

@@

# Plot adult perf for pccc by cod
fig_pccc_cod_adult <- plot_perf_bar(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Adult Causes of Death, 12+ Years (n=", n_adult, ")"),
    text_scale = 0.7,
    x_hpos = -0.15,
    x_expand = expansion(add = 0.15)
)

@@

# Plot child perf for pccc by cod
fig_pccc_cod_child <- plot_perf_bar(
    df_long %>% filter(age == "child"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Child Causes of Death, 28 Days to 11 Years (n=", n_child, ")"),
    text_scale = 0.92,
    x_hpos = -0.24,
    x_expand = expansion(add = 0.25)
)

@@

# Plot neo perf for pccc by cod
fig_pccc_cod_neo <- plot_perf_bar(
    df_long %>% filter(age == "neo"),
    calc_pccc,
    group = "cod_name",
    title = paste0("Neonatal Causes of Death, <28 Days (n=", n_neo, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.92,
    x_hpos = -0.24,
    x_expand = expansion(add = 0.25)
)

@@

# Plot perf trend over age ranges
fig_pccc_age <- plot_perf_trend(
    df_long %>%
        mutate(
            age_range = str_replace(age_range, " ", "\n") %>%
                factor(., levels = age_levels)
        ),
    y_title = "Partial Chance Corrected Concordance (PCCC)",
    text_scale = 0.9,
    y_limits = c(0.2, 0.9),
    y_breaks = seq(0, 1, by = 0.05),
)
